% check the thing which needed articulating better!!
The `slingshot' is a form of argument which shows that all true sentences have the same reference.
This conclusion has been used argue against fact-based and similar correspondence theories of truth, to motivate either non-facts based correspondence theories, or rejecting correspondence entirely.

Against this I argue that the conclusion of the slingshot argument is compatible with facts-based and similar correspondence theories of truth.
First I will explain Davidson's `Great Fact' formulation of the slingshot, a typical example of the argument.
Secondly, I show that in its most basic form, the correspondence theory is compatible with the conclusions of this argument.
Any formulation of correspondence theory which \emph{is} incompatible must then be so because of some further commitment.
I argue that the intuitions which would motivate such commitments are false, so there is no incompatibility.
In some respects such intuitions actually accord with the slingshot's conclusions.
Finally I consider some further implications of the slingshot for a compatible correspondence theory and sketch the outline of such a theory.

Since the slingshot is meant to challenge correspondence theory significantly, this paper is meant to defend it significantly.

I use the term \textit{truthbearer} for a thing which is true or false (often thought to be sentences, propositions, beliefs etc.)
A \textit{truthmaker} makes a truthbearer true or false (often thought facts, states of affairs etc.).
This terminology is meant to be neutral on what truthmakers or truthbearers actually are, because I am defending correspondence theory in general from the slingshot in general, regardless any particular formulation of either.

Correspondence theory is a group of theories sharing the view that truth is a relation (`correspondence') with a truthmaker in the real world (a fact, a state of affairs etc.).
This is motivated intuitively: truth seems to be about what \emph{is the case} in the world, and true truthbearers seem to be `made true' somehow (e.g.\ by corresponding with a fact).

This also agrees with the monistic intuition that truth has a single nature---here that of correspondence with a truthmaker.

The slingshot is a form of argument showing that all sentences with the same truth value have the same reference. % same REFERENCE or same REFERENT?
% I need to choose and consistently stick to 'correspondence WITH' OR 'correspondence TO'
It can be extended to show that if correspondence theory is true, then all sentences with the same truth value must correspond to the same truthmaker.
The version of the slingshot presented here is Davidson's.
\parencite[753]{Davidson_1969}
Davidson assumes facts are sentences' truthmakers,\footnotemark but the argument can be constructed with any truthmaker (propositions, states of affairs etc.)
\parencite[752]{Davidson_1969}
\footnotetext{
It might seem that if sentences have truthmakers, then they must be truthbearers.
% It would be good to include what Davidson HIMSELF thinks here. (does he think that sentences are true primarily or secondarily?)
This would be consistent with Davidson's theory, but a more common view is that sentences are only true or false (and so only have truthmakers) \emph{secondarily}---in virtue of \emph{primary} truthbearers that sentences express or otherwise correspond to.
On many theories, these primary truthbearers are propositions.
}

The argument assumes:
\parencite[753]{Davidson_1969}

	\begin{principle}{Reference}\label{srefer}
	Sentences refer (like names or definite descriptions do).
	\end{principle}

	\begin{principle}{Equivalence}\label{sameref}
	Logically equivalent singular terms (including sentences) refer to the same thing.
	\end{principle}

	\begin{principle}{Substitutivity}\label{constref}
	% this could maybe be made more clear?
	What a complex singular term refers to will not change if a part of it which is a singular term is substituted with another singular term with the same reference.
	\end{principle}


Given these assumptions and any sentences $P$ and $Q$ with the same truth value, the argument runs as follows.

This sentence must refer to whatever $P$ refers to, and will be true iff $P$ is true:

	\begin{example}\label{setP}
	The set of all objects which are identical with themselves and (for which) $P$ obtains is identical with the set of all objects which are identical with themselves.
	\end{example}

All things are identical with themselves, so the `set of all objects which are identical with themselves and (for which) $P$ obtains' will just be the set of all things if $P$ is true, and the empty set otherwise.
The whole sentence says that this set is identical with the set of all objects, so \ref{setP} is true iff the first set is the set of all objects.
So \ref{setP} is true iff $P$ is true so they are logically equivalent.
Since \ref{setP} is logically equivalent with $P$, they must have the same reference (\ref{sameref}).
Hence, `$P$' can be substituted for \ref{setP}.
(\ref{constref})

Applying this conclusion to sentences about correspondence with truthmakers, we show that the statement that $P$ corresponds with the fact that $Q$.
First, correspondence theory entails the following sentence:

	\begin{example}\label{stateP}
	the statement that $P$ corresponds with the fact that $P$.
	\end{example}

From this, and the fact that $P$ can be substituted for \ref{setP}, \ref{factP} can be derived:

	\begin{example}\label{factP}
	the statement that $P$ corresponds with the fact that the set of all objects which are identical with themselves and (for which) $P$ obtains is identical with the set of all objects which are identical with themselves.
	\end{example}

Next, for similar reasons to above $Q$ is logically equivalent with:

	\begin{example}\label{setQ}
	The set of all objects which are identical with themselves and (for which) $Q$ obtains is identical with the set of all objects which are identical with themselves.
	\end{example}

The expression `the set of all objects which are identical with themselves and (for which) $Q$ obtains' can be constructed from it's counterpart in \ref{setP}, only by substituting $Q$ for $P$.
The reference of that expression depends only on the truth value of the sentence $P$ or $Q$ in it (it will be all objects if $P$ or $Q$ is true, and no objects / the empty set if $P$ or $Q$ is false).
Since $Q$ and $P$ have the same truth value, the expression with `$Q$' must have the same refer as it's counterpart in \ref{setP} (`the set of all objects which are identical with themselves and (for which) $P$ obtains').

This expression is the only difference between \ref{setP} and \ref{setQ}.
Hence, \ref{setQ} is constructed from \ref{setP} by substituting a singular term with the same reference, so \ref{setQ} must have the same reference as \ref{setP}.
(\ref{constref})
Since they have the same reference, \ref{setP} and \ref{setQ} can be substituted in \ref{factP} to produce \ref{factQ}:
(\ref{constref}) 

	\begin{example}\label{factQ}
	the statement that $P$ corresponds with the fact that the set of all objects which are identical with themselves and (for which) $Q$ obtains is identical with the set of all objects which are identical with themselves.
	\end{example}

Finally, by reversing the initial step from \ref{stateP} to \ref{factP}, we derive \ref{statePQ}:

	\begin{example}\label{statePQ}
	the statement that $P$ corresponds with the fact that $Q$.
	\end{example}

Since this will work for any two sentences with the same truth value, all true sentences must be made true by the same truthmaker. (which Davidson calls the `Great Fact'.)
\parencite[753]{Davidson_1969}
% some more examples here would be good...!
Others have identified it with truth \parencite[216]{Frege_1948} or the `kind of total state of affairs we call a world' \parencite[242]{Lewis1943-LEWTMO}.

% a list / overview paper (if one exists) would be handy here!
% Many objections can be made to this argument in itself, but this paper is not concerned with them.

This conclusion is compatible with correspondence theory.
The correspondence theory does not say that all true sentences do \emph{not} correspond to the same truthmaker (though this would be in the spirit of the motivating intuitions).
The point is just that for a truthbearer to be true just is for it to correspond to the relevant truthmaker---even if there is only one such truthmaker.
Most reasonable formulations of correspondence theory would allow for the possibility of at least some different truthbearers having the same truthmakers.
For example, sentences which express different things about one aspect of the nature of an object (e.g. `the apple is red' and `the apple is not blue')	could reasonably be thought to be different truthbearers, but be made true by the same truthmaker.
% this could be forumulated better: a premise which MAKES the correspondence theory incompatible with the conclusion.
% So a further premise is needed: that the correspondence theory is in some way incompatible with the conclusions of the slingshot argument:
So a further premise is needed which makes the correspondence theory incompatible with the conclusion of the slingshot argument.

	\begin{principle}{Incompatibility}\label{incompatible}
	Not all true truthbearers are made true by the same truthmaker.
	\end{principle}

% yyou could use 'seems faily likely' rather than 'motivated by intuition'
\ref{incompatible} is motivated by the intuition that true sentences which correspond with the same truthmaker are similar in some way (other than \emph{just} corresponding with the same truthmaker) that not all true sentences are.
% Put another way: we think intuitively that true sentences actually differ in some respect, but if all true sentences had the same truthmaker, then they would not so differ.
Put another way: we think intuitively that some (perhaps most) true sentences actually differ in some respect, which sentences with the same truthmaker cannot differ in.
For example, one might think different true sentences mean different things, but sentences with the same truthmaker always mean the same thing.
The conclusion of the slingshot argument then shows all true sentences mean the same thing, which seems very unlikely.
\footnote{
Some radical theorists might accept some such unlikely views though.
To really be sure of \ref{incompatible} an argument would be needed to show that there are true truthbearers made true by different truthmakers.
The line of reasoning above for example would need a further premise: that there at least two true sentences which differ in meaning.
Then such sentences would have to have different truthmakers, demonstrating \ref{incompatible}.
}
Or if truthbearers were known to be structurally isomorphic or similar to their truthmakers and the structures of truthbearers varied, then they could not share a truthmaker.
Similar constradictions could be derived with other differences that truthbearers have, but supposedly could not have if they had the same truthmaker.

Davidson expresses a similar sentiment: if two sentences correspond to the same thing then the statement of each is `identical' with that of the other.
Since not all true sentences state identical things, Davidson takes this as a reduction to absurdity of facts-based correspondence theory.
\parencite[750]{Davidson_1969}

However, the above intuition and Davidson's articulation of it are false.
Just because two sentences have the same truthmaker, they need not mean the same (as in the intuitive version), state identical things (Davidson's version) or generally have anything else `important' in common.
For example, if I have just eaten an apple and it has been my only one this week, then the following two sentences have the same truth maker:

	\begin{example}\label{yesterday}
	I ate an apple yesterday.
	\end{example}

	\begin{example}\label{week}
	I have eaten an apple this week.
	\end{example}

% This is the part which needs the most work / expansion!
On the slingshot argument this truthmaker will be the Great Fact.
Alternatively it will be the fact (or proposition etc.) that I just ate a apple.
Whatever it is, the truthmaker will be the same for the two sentences, but they mean different things and have different contents in other respects.
% They have different semantically significant parts (`yesterday', `this week') and different meanings (one could be true and the other false, if I had eaten an apple today, but not yesterday, so the two cannot mean the same).
They have different semantically significant parts (`yesterday', `this week').
They mean different things: one could be true and the other false if I had eaten an apple today but not yesterday, so the two cannot mean the same.
% LW And so, although they correspond to the same fact, they need not have done. These modal considerations should make us suspicious of the slingshot - we know that definite descriptions cannot generally be substituted for one another in modal contexts.

Generalising this, even if all true sentences have the same truthmaker, they may differ in other important respects: their semantically significant parts, their meanings, etc.

I do not think there is any respect other than truth in which sentences with the same truthmaker must be the same but in which sentences actually differ. 
If there were then sentences like \ref{yesterday} and \ref{week} would have to be similar in this regard, but I cannot find any such regard in which they must be so.
They can mean different things, concern different subjects and objects, have sentential structure and content, and can have different pragmatics when uttered.
Thus it is not a problem for correspondence theory that all true sentences have the same truthmaker.
In fact Frege---whom Davidson follows in his argument \parencite[750]{Davidson_1969}---embraced a similar conclusion without seeing it as a problem.
He thouht that all true sentences referred (as whole sentences) to The True, the analog of Davidson's Great Fact.
\parencite[216]{Frege_1948}

This should perhaps not be surprising.
The expressed meaning of apparently identical sentences (the same words in the same order) can differ significantly because of their pragmatics.
The final communication includes things determined by considerations beyond the apparent semantics. 
Why should we be surprised if sentences which have identical truthmakers have significant differences in their meaning (or other semantically relevant qualities) determined by things beyond those truthmakers?

Of course this means that all true sentences are true `together' in various ways: all true sentences will be true in the same way, in virtue of the same truthmaker etc.
This is in accord with the monistic intuition which correspondence theory began with.
True sentences might mean or express different things, but all true sentences share a common nature in their truth.
So this consequence accords with our intuitions too.

These conclusions will put bounds on the correspondence theory in general---or at least on any semantic theory which accepts it.
I see two major issues for such theories to tackle. % better wording here?

The first is meaning.
% maybe 'many things thought to be truth bearers are often... thought...'
Truthbearers are generally thought also to be \textit{meaningbearers} (things which mean something, like sentences)\footnotemark, or to be meanings themselves (like propositions).
\footnotetext{If truthbearers have meanings, they would almost certainly only be a subset of meaningbearers.
There are clearly things with meanings---words, predicates, names etc.---which are not true or false.}
% this really needs articulating better!
Plausibly, the sources of meaning and truth have something in common: a sentence like `the apple is red' might be thought to mean that that apple over there is red, and to be made true by the apple being red (by what the sentence means being the case, or being true).
Both the truthmaker and the meaning depend on the actual apple and its properties.
This is one motivation for \ref{incompatible}.
But if all truthbearers (all of which are menaingbearers) have the same truthmaker then it might appear that they all mean the same thing.\footnotemark\ 
Clearly not all true sentences mean the same thing, so a correspondence theory which accepts the above arguments must be compatible with an account of meaning which allows sentences to mean different things even with the same truthmaker.
\footnotetext{%{{{
Some theories could attempt to dissolve the question entirely.
It is a common view that propositions are primary truthbearers, and sentences mean propositions.
Propositions are \emph{what is meant} by sentences, but do not mean anything themselves.
Sentences are not true or false themselves, only in virtue of the propositions they express.
If the sense in which sentences are not themselves true or false is strong enough, then the problem is dissolved: no (primary) truthbearer has any meaning, so the question of whether their meanings differ never arises.
This is not a promising view though, because declarative sentences do seem to be `properly' true or false, even if only secondarily.
}%}}}

This is a particular case of the motivation for \ref{incompatible} above, and can be answered similarly.
On any correspondence theory, it is clear that some truthbearers with the same truthmaker can mean different things as \ref{yesterday} and \ref{week} do.
Even if all truthbearers had the same truthmaker, they could still differ in meaning.
This semantic theory just has to give an account of meaning beyond (though not necessarily excluding) the truthmaker of a meaning-bearing truthbearer.
Even if the conditions of meaning include the truthmaker, they must include more besides.

There are a number of ways a theory could account for this.
Frege thought that the meaning of a meaningbearer included its sense.
\parencite[210]{Frege_1948} 
On this theory sentences also have a referent (truth or falsehood), and many such senses could all be associated with the same referent.
Braun develops a similar theory regarding the expression of propositions: that the same proposition can be expressed or believed in different `ways'.
Braun developed this view in a theory of empty names, but a similar view could be used to explain differences in meaning between truthbearers.
Even if a truthbearer's meaning were partially determined by its truthmaker, it could bear this truth in different ways as Braun's sentences express the same proposition in different ways.

I think many such accounts---where the meaning of a meaningbearer is partly determined by \emph{how} it is meant, not just \emph{what} is meant---are very plausible.

The second issue is the relation of correspondence itself.
Many correspondence theories hold that the correspondence relation between a truthbearer and its truthmaker is isomorphism: for the two to correspond is for the truthbearer to be isomorphic with the truthmaker.
If this were true, and all truthbearers had the same truthmaker, then they would all be isomorphic with it.
Isomorphism is transitive and symmetric, so all truthbearers would be isomorphic with each other.
But it seems very unlikely that all truthbearers \emph{are} isomorphic with each other.
Certainly sentences and propositions---the two most likely candidate truthbearers---are not.

So correspondence theory must also provide an account of the correspondence relation which is compatible with the conclusions of the argument above.
The correspondence relation must be explained either as a relation which is symmetric and transitive, and which all truthbearers have alike, or a relation which is not symmetric, not transitive, or both and they do \emph{not} all have alike.

I think the second is more likely.
Whatever they are, truthbearers and truthmakers are likely to be very different in important respects---propositions are very different from states of affairs.
Just because truthbearers relate in some way to truthmakers, truthmakers need not similarly relate to truthbearers.
A plausible candidate relation is representation: truthbearers are true when they represent the truthmaker.
This would be especially likely if the truthmaker were something like `the actual state of affairs'.
But anything like the actual state of affairs will not represent propositions or sentences, so the relation is non-symmetric.
On an account like this the issue is solved: different truthbearers all correspond with the truthmaker by representing it, but each could represent it in a different way.
Because representation is non-symmetric, the account does not entail that truthbearers all represent each other.

Of course the first option is also formally possible.

This produces the outline of a correspondence theory which is compatible with the slingshot's conclusions.
All true truthbearers correspond with the same truthmaker.
Truthbearers' meaning is at least partially determined something other than their truthmakers.
The correspondence relation between truthbearers and truthbearers is not isomorphism, and is probably a non-symmetric.

Such a theory is not implausible, and should give pause to those who think the slingshot is a knockdown argument for the correspondence theory.
